\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[default]{raleway}
\usepackage{hyperref}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\usepackage[a4paper,top=1.5cm,bottom=1cm,left=1.5cm,right=1.5cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{12pt}
\lhead{}
\chead{\small{Hugh Thomson Comer $\cdot$ Principal Cloud Engineer $\cdot$ \href{mailto:thomcom@gmail.com}{thomcom@gmail.com} $\cdot$ 970 310 5396}}
\rhead{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\parindent}{0mm}
\usepackage{array}
\usepackage{color}
\definecolor{sectcol}{RGB}{243,243,243}
\definecolor{bgcol}{RGB}{150,180,210}
\definecolor{softcol}{RGB}{225,225,225}
\newcommand{\cvsection}[1]{\vspace{8pt}\colorbox{sectcol}{\makebox[1\linewidth][l]{\textbf{#1}}}\vspace{2pt}}
\newcommand{\cvevent}[3]{\begin{tabular*}{\textwidth}{p{2.5cm} p{7.5cm} r{5.5cm}}\textbf{#1} & \textbf{#2} & \textbf{#3}\end{tabular*}\vspace{2pt}}
\newcommand{\cvdetail}[1]{\begin{tabular*}{\textwidth}{p{2.5cm} p{14.5cm}} & $\bullet$ #1\end{tabular*}\vspace{2pt}}
\newcommand{\mystrut}{\rule[-.7\baselineskip]{0pt}{\baselineskip}}

\begin{document}
\pagestyle{fancy}

\vspace{-10pt}
\colorbox{bgcol}{\makebox[\linewidth][c]{\HUGE{\textcolor{white}{\textsc{Hugh Thomson Comer}}}}}

\cvsection{Summary}
\cvdetail{Architect GPU-accelerated platforms for agentic AI and RAG-powered search, scaling NVIDIA’s analytics and visualization tools to enterprise-grade production. Expertise in CUDA, Python, Kubernetes, and cloud-native systems drives end-to-end development of GenAI solutions.}

\cvsection{Technical Skills}
\cvdetail{\textbf{Languages}: Python, TypeScript, C++, CUDA, R, LaTeX}
\cvdetail{\textbf{Platforms}: *nix, Docker, GitHub, AWS, GCP, Kubernetes}
\cvdetail{\textbf{Frameworks}: RAPIDS, cuDF, cuSpatial, React, Flask}
\cvdetail{\textbf{Domains}: Parallelization, Machine Learning, Computer Vision, LLM/RAG}
\cvdetail{\textbf{Activities}: Open-Source Contributor (GeoArrow, cuDF), Technical Mentor, Astronomy}

\cvsection{Professional Experience}
\cvevent{10/18 – Present}{Senior Library Software Engineer}{NVIDIA}
\cvdetail{Authored CUDA/Python kernels for cuDF and created cuSpatial, delivering 15–100× faster geospatial joins and trajectory ops, driving open-source adoption.}
\cvdetail{Architected cloud-native Kubernetes stack with Helm for GPU-accelerated vector search, optimizing pod scheduling for Pixels Video-Search Blueprint, a candidate for GenAI search products.}
\cvdetail{Built browser/server pipelines streaming multi-million-row data frames to WebGL for sub-second visual analytics, now a reference for real-time dashboards.}
\cvdetail{Integrated RAG workflows into agentic AI prototypes for enterprise search and chatbot applications, drafting patents on GPU-accelerated vector search.}
\cvdetail{Mentored 5+ engineers in CUDA and Kubernetes best practices, enforcing typed interfaces and property-based tests for cuDF and cuSpatial.}
\cvdetail{Co-designed GeoArrow columnar spec with GeoPandas team; authored Python/Cython wrappers for KvikIO + nvCOMP for direct-to-GPU I/O and compression.}

\cvevent{01/12 – 10/18}{Mobile Technical Lead Engineer}{Cardinal Peak, LLC}
\cvdetail{Led mobile app and cloud development, focusing on system architecture and performance optimization.}

\cvevent{05/08 – 10/10}{Software Engineer}{Mersive Technologies, Electric Textiles}
\cvdetail{Developed GPU-accelerated algorithms and system designs for visualization and games.}

\cvsection{Education}
\cvevent{2005 – 2009}{M.Sc. Computer Science}{Colorado State University}
\cvdetail{Thesis: Automatic Prediction of Interest Point Stability (Computer Vision)}

\cvevent{1996 – 2003}{B.A. Communications}{Western State College}
\cvdetail{Emphasis in Technical Communication and Computer Science}

\vspace*{\fill}
\colorbox{bgcol}{\makebox[\linewidth][c]{\small Hugh Thomson Comer \href{mailto:thomcom@gmail.com}{thomcom@gmail.com} \href{https://www.linkedin.com/in/thomcom}{linkedin.com/in/thomcom} $\cdot$ \href{https://github.com/thomcom}{github.com/thomcom}}}

\end{document}